---
title: "Example Report"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      error = FALSE)
```

```{r}
library(InvestR)
library(ggplot2)
library(kableExtra)
data("ExampleReport")
fund_bench <- combine_xts(fund, bench)
plot_col <- c('firebrick', 'dodgerblue', 'goldenrod', 'seagreen3')
```

\newpage

# Performance Summary

```{r, fig.height=9, fig.width=7}
viz_perf(fund_bench, plot_col = plot_col)
```

\newpage

# Performance Summary

## Periodic Returns

Returns as of `r zoo::index(fund_bench)[nrow(fund_bench)]` (periods greater 
than one year are annualized)

```{r}
cal_ret <- tbl_cal_perf(fund_bench)
kbl <- kable(cal_ret$fmt[, 1:10], align = rep('r', 10))
kbl_in <- kable_styling(kbl, latex_options = 'striped')
row_spec(kbl_in, 0, align = 'c', background = '#104E8B', color = 'white', bold = TRUE)
```

\vspace{15pt}

## Calendar Returns

Fund Ticker `r colnames(fund)[1]`

```{r}
mon_ret <- tbl_month_ret(fund, dig = 2)
kbl <- kable(mon_ret$fmt, align = rep('r', 14))
kbl_in <- kable_styling(kbl)
kbl_in <- column_spec(kbl_in, 14, bold = TRUE)
row_spec(kbl_in, 0, align = 'c', background = '#104E8B', color = 'white', bold = TRUE)
```

\newpage

## Key Performance Metrics

From `r zoo::index(fund_bench)[1]` to `r zoo::index(fund_bench)[nrow(fund_bench)]`

```{r}
res <- tbl_perf_stat(fund, bench, rf)
kbl <- kable(res$fmt)
kbl_in <- kable_styling(kbl, latex_options = 'striped')
row_spec(kbl_in, 0, align = 'c', background = '#104E8B', color = 'white', bold = TRUE)
```

\vspace{15pt}

```{r, fig.width=7}
viz_capm(fund_bench) +
  scale_color_manual(values = plot_col) +
  theme(legend.position = 'bottom')
```

# Risk

## Drawdowns

```{r}
viz_drawdown(fund_bench, 'months') +
  scale_color_manual(values = plot_col) +
  theme(legend.position = 'bottom')
viz_drawdown(fund, 'months') +
  scale_color_manual(values = plot_col) +
  theme(legend.position = 'bottom')
```

\newpage

## `r colnames(fund)[1]` 10 Worst Drawdowns

```{r}
res <- tbl_drawdowns(fund)
rownames(res$fmt) <- NULL
kbl <- kable(res$fmt)
kbl_in <- kable_styling(kbl, latex_options = 'striped')
row_spec(kbl_in, 0, align = 'c', background = '#104E8B', color = 'white', bold = TRUE)
```

## Historical Value at Risk (Annualized)

```{r}
res <- tbl_risk_quantile(fund_bench)
kbl <- kable(res$fmt)
kbl_in <- kable_styling(kbl, latex_options = 'striped')
row_spec(kbl_in, 0, align = 'c', background = '#104E8B', color = 'white', bold = TRUE)
```

`r colnames(fund)[1]` Monthly Historical Value at Risk Plot

```{r, fig.height=4}
x <- change_freq(fund, 'months')
viz_pdf_risk(x)
```

# Style

Rolling Weekly Style Analysis

```{r, fig.height=4}
res <- viz_style_drift(fund, style_ind)
res$style_plot
```

```{r, fig.height=4}
res$comp_plot
```